Variable Selection

### 2015-08-21 Regression.rmd
getting somewhere with regression

# library('knitr', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('ggplot2', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
# library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
# library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
# library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
# library('car', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('fpc', lib='C:/Progra~1/R/R-3.2.1/library')
# library('vegan', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library(devtools,lib='C:/Progra~1/R/R-3.2.1/library')

@@

# 
# setwd("~/OneDrive/shared files/Bligh Tanner/masters/data")
# setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
# opts_knit$set(root.dir= "C:/Users/n9232371/Documents/Consultbusiness/data")
# all7c<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all7c.csv')[,-1]
all7c<- read.csv('~/OneDrive/shared files/Bligh Tanner/masters/data/all7c.csv')[,-1]
all7c$Post.Code<- as.factor(all7c$Post.Code)

@@

inv.mlsto
timespan
no.users
Discipline
pc.pro
client.totinv
code.director
Num.disc
Business
Biz.type

@@

code.contact
code.client
Project.Value
JD.Second
Post.Code
code.ProjEng
Billing.Type
majority.pos
pc.majpos

@@

* code.contact: 1652 NA
* code.client: 422 NA
* Project.Value: 2333 NA
* JD.Second: 1057 NA
* Post.Code: 356 NA
* code.ProjEng: 47 NA
* Billing.Type: 1314 NA
* majority.pos: 377 NA
* pc.majpos: 377 NA

```{r echo=FALSE}
some <- all7c %>% select(return.pdol, mlsto, inv.mlsto, timespan,no.users,Discipline,pc.pro,
                         client.totinv,code.director,Num.disc,Business,Biz.type,
                         code.contact,code.client,Project.Value,JD.Second,Post.Code,code.ProjEng,Billing.Type,majority.pos,
                         pc.majpos)

@@

experiment<- sapply(some, function(x) is.na(x))
NA.plot<- melt(experiment)
NA.plot$mlsto<- rep(all7c$mlsto, ncol(experiment))
#reorder levels for ggplot by total number of NA TRUE
# table(NA.plot$Var2, NA.plot$value)[,'TRUE']
NA.plot <- within(NA.plot, 
                         Var2 <- factor(Var2, 
                                               levels=names(sort(table(NA.plot$Var2, NA.plot$value)[,'TRUE'], 
                                                                 decreasing=FALSE))))

@@

>>>>

library('knitr', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('ggplot2', lib = 'C:/Progra~1/R/R-3.2.1/library')
library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
library('caret',lib='C:/Progra~1/R/R-3.2.1/library')
# library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
library('car', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('fpc', lib='C:/Progra~1/R/R-3.2.1/library')
# library('vegan', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library(devtools,lib='C:/Progra~1/R/R-3.2.1/library')

@@

# 
# setwd("~/OneDrive/shared files/Bligh Tanner/masters/data")
# setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
# opts_knit$set(root.dir= "C:/Users/n9232371/Documents/Consultbusiness/data")
all7d<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all7d.csv')[,-1]
all7d<- read.csv('~/OneDrive/shared files/Bligh Tanner/masters/data/all7d.csv')[,-1]
all7d$Post.Code<- as.factor(all7d$Post.Code)

@@

inv.mlsto
timespan
no.users
Discipline
pc.pro
client.totinv
code.director
Num.disc
Business
Biz.type
code.ProjEng

@@

code.contact
code.client
Project.Value
JD.Second
Post.Code
Billing.Type
majority.pos
pc.majpos

@@

* code.contact: 1652 NA
* code.client: 422 NA
* Project.Value: 2333 NA
* JD.Second: 1057 NA
* Post.Code: 356 NA
* Billing.Type: 1314 NA
* majority.pos: 377 NA
* pc.majpos: 377 NA

```{r echo=FALSE}
some <- all7d %>% select(return.pdol, mlsto, inv.mlsto, timespan,no.users,Discipline,pc.pro,
                         client.totinv,code.director,Num.disc,Business,Biz.type,
                         code.contact,code.client,Project.Value,JD.Second,Post.Code,code.ProjEng,Billing.Type,majority.pos,
                         pc.majpos)

@@

experiment<- sapply(some, function(x) is.na(x))
NA.plot<- melt(experiment)
NA.plot$mlsto<- rep(all7d$mlsto, ncol(experiment))
#reorder levels for ggplot by total number of NA TRUE
# table(NA.plot$Var2, NA.plot$value)[,'TRUE']
NA.plot <- within(NA.plot, 
                         Var2 <- factor(Var2, 
                                               levels=names(sort(table(NA.plot$Var2, NA.plot$value)[,'TRUE'], 
                                                                 decreasing=FALSE))))

@@

Will address each of the variables with many nA separately. 8 of these variables totally. run a separate lm for each of these

Need to transform some numeric variables:

return.pdol - cube root
inv.mlsto - log
timespan - cube root
pc.pro - leave alone
client.totinv - log

Project.Value - log
pc.majpos - log

```{r, echo=FALSE}

#write a function for testing transformations

trans<- function(var= 'timespan', df= all7d, transform = 'cbrt'){
        #initial q plot
        init<- qqPlot(df[,var], 
                       main = 'untouched variable')
        print(init)

        #make trial dataframe
        trial = sapply(df[,var], function(x){
                if(transform == 'log'){
                        log(x)
                } else

                if(transform == 'neglog')
                        {
                        sign(x)*log(abs(x) + 1)
                } else

                if(transform == 'sqrt')
                {
                        sqrt(x)
                } else
                        if(transform == 'cbrt')
                {
                        sign(x) * abs(x)^(1/3)
                } else
                { x^2 }

                }) %>% 
                as.data.frame

        colnames(trial)[names(trial) %in% '.']<-'trans.var'

        #qplot for transformation
        qqtrans<- qqPlot(trial$trans.var, 
                         main = 'transformed')
        print(qqtrans)

        ##move on to density plots

        #original variable
        dens<- ggplot(df, aes_string(x=var)) + geom_histogram(aes(y=..density..))
        print(dens)

        #transformed variable
        dens.trans<- ggplot(trial, aes_string(x='trans.var')) + geom_histogram(aes(y=..density..))
        print(dens.trans)
}

trans(var= 'timespan', df= all7d, transform = 'cbrt')
trans(var= 'inv.mlsto', df= all7d, transform = 'log')
trans(var= 'return.pdol', df= all7d, transform = 'cbrt')
trans(var= 'pc.majpos', df= all7d, transform = 'log')
trans(var= 'client.totinv', df= all7d, transform = 'log')
trans(var= 'Project.Value', df= all7d, transform = 'log')

Have now decided on transformations for numeric variables.

Create all7d ready for linear regression analysis

```{r, echo=FALSE}

math.cbrt <- function(x) {
        sign(x) * abs(x)^(1/3)
}

all7d$timespan.cbrt<- math.cbrt(all7d$timespan)
all7d$inv.mlsto.log <- log(all7d$inv.mlsto)
all7d$client.totinv.log <- log(all7d$client.totinv)
all7d$Project.Value.log <- log(all7d$Project.Value)
all7d$pc.majpos.log <- log(all7d$pc.majpos)

Root mean square error as initial check. Write code which transforms response variable back to original format by cubing, then finds RMSE.

```{r, echo=FALSE}

#predict Petal.Width using lm, find RMSE
#answer will be return.pdol
#guess will be response of prediction which is cube root
RMSE<- function(answer, guess){
        error= answer-guess
        root.error= sqrt(mean(error^2))
        print(root.error)
}

Now fit full variables to linear regression

```{r, echo=FALSE}

full = lm(return.pdol ~ 
                  inv.mlsto.log + timespan.cbrt + no.users + Discipline + pc.pro + client.totinv.log + code.director + 
                  Num.disc + Business + Biz.type + code.ProjEng,
          data = all7d)
summary(full)

#have a look at the residuals

res<- resid(full)
plot(all7d$inv.mlsto.log, res)
abline(0,0)

plot(density(res))
qqPlot(res)

#compare some of the answers
ans<- data.frame(answer= all7d$return.pdol, full.lm = predict(full, all7d, interval= 'predict'))

RMSE(ans$answer, ans$full.lm.fit)

RMSE is 0.4768 which isn't great in terms of predicting return per dollar.
R^2 is 0.1905

Let's try deleting some full variables

```{r, echo=FALSE}
full.2<- update(full, .~. -client.totinv.log)
summary(full.2)
full.3<- update(full.2, .~. -code.director)
summary(full.3)
full.4<- update(full.3, .~. -Num.disc)
summary(full.4)
full.5<- update(full.4, .~. -code.ProjEng)
summary(full.5)
full.6<- update(full.5, .~. -Biz.type + Discipline)
summary(full.6)

#RMSE check

ans<- data.frame(answer= all7d$return.pdol, full.lm = predict(full.6, all7d, interval= 'predict'))

RMSE(ans$answer, ans$full.lm.fit)

Feels better. That leaves us with

* inv.mlsto.log
* Discipline
* timespan.cbrt
* no.users
* pc.pro
* Discipline
* Business

RMSE = 0.48266

Going back to full variables, lets try pairwise multiplying..

```{r, echo=FALSE}
#try diff pairs

pairs.lm<- lm(return.pdol ~ inv.mlsto.log + Discipline + timespan.cbrt + no.users + pc.pro + Business + 
                      inv.mlsto.log*pc.pro + inv.mlsto.log*Business,
              data=all7d)

summary(pairs.lm)
pairs<- predict(pairs.lm, all7d)
ans<- data.frame(answer= all7d$return.pdol, pairs.lm = pairs)

RMSE(ans$answer, ans$pairs.lm)

#down to 0.4759

Let's try adding more variables:

```{r, echo=FALSE}
#try adding code.client

addone<- function(var= 'JD.Second', df= all7d){
        reduced = df[!(is.na(df[,var])),]
        formula = paste("return.pdol ~ inv.mlsto.log + timespan.cbrt + no.users + Discipline + pc.pro + inv.mlsto.log*pc.pro + inv.mlsto.log*Business", var, sep=" + ")
        add.one = lm(as.formula(formula), data = reduced)

        print(summary(add.one))

        ans= data.frame(answer= reduced$return.pdol, addone.lm = predict(add.one, reduced, interval= 'predict'))

        print(head(ans))

        print(
        paste("RMSE=", RMSE(ans$answer, ans$addone.lm.fit) %>% round(4), sep= " ")
        )

}

#without additional variables, RMSE sits at 0.4759

addone(var='JD.Second', df=all7d)
#RMSE = .4709
addone(var='Post.Code', df=all7d)
#RMSE = .4353
addone(var='majority.pos', df=all7d)
#RMSE = .4541
addone(var='pc.majpos.log', df=all7d)
#RMSE = .4553
addone(var='code.client', df=all7d)
#RMSE = .4394
addone(var='Billing.Type', df=all7d)
#RMSE = .4579
addone(var='code.contact', df=all7d)
#RMSE = .3972

#dont use post code ever. 
#JD.Second doesn't help that much. acutally makes RMSE worse.

Delete Post.Code option

Billing.Type should be paired with inv.mlsto and maybe Discipline

maybe client should be paired with inv.mlsto
maybe JD.Second should be paired with inv.mlsto and code.client and timespan and pc.pro and no.users?? which ever one does something.

majority.pos pair with inv.mlsto
pc.majpos pair with inv.mlsto

Write a function that lists the extra variable you're trying and write out the interaction.

```{r, echo=FALSE}

addmult<- function(var= c('JD.Second', 'code.client'), combos= c('JD.Second*inv.mlsto.log'), df= all7d){
        reduced = df[complete.cases(df[,var]),]
        formula = paste("return.pdol ~ inv.mlsto.log + timespan.cbrt + no.users + Discipline + pc.pro + inv.mlsto.log*pc.pro + inv.mlsto.log*Business")

        for(i in 1:length(var)){
                formula = paste(formula, var[i], sep= " + ")
        }

        for(i in 1:length(combos)){
                formula = paste(formula, combos[i], sep= " + ")
        }

        add.one = lm(as.formula(formula), data = reduced)

        print(summary(add.one))

        ans= data.frame(answer= reduced$return.pdol, addone.lm = predict(add.one, reduced, interval= 'predict'))

        print(head(ans))

        print(
        paste("RMSE=", RMSE(ans$answer, ans$addone.lm.fit) %>% round(4), sep= " ")
        )

}

#try Billing.Type with inv.mlsto.log
addmult(var= c('Billing.Type'), combos= c('Billing.Type*inv.mlsto.log'), df= all7d)
# no

#try code.client*inv.mlsto.log
addmult(var= c('code.client'), combos= c('code.client*inv.mlsto.log'), df= all7d)
#made a difference, brought RMSE down to .4076 :)!

#try JD.Second with inv.mlsto.log (no), code.client (too intense), timespan (no), pc.pro (no), no.users (yes)?
addmult(var= c('JD.Second'), combos= c('JD.Second*no.users'), df= all7d)
#add JD.Second*no.users

addmult(var= c('majority.pos'), combos= c('majority.pos*inv.mlsto.log'), df= all7d)
#no

addmult(var= c('pc.majpos.log'), combos= c('pc.majpos.log*inv.mlsto.log'), df= all7d)
#no

It is worthwhile to include:

* code.client by inv.mlsto.log because brought down RMSE from 0.4394 (code.client) to 0.4076 (code.client + code.client by inv.mlsto.log)
* JD.Second by no.users. Brought down RMSE from 0.4709 to 0.4612...

Now look at cross validation for full variable set:

```{r, echo=FALSE}

#using caret package
tc <- trainControl("cv",10,savePred=F)
fit<- train(return.pdol ~ inv.mlsto.log + Discipline + timespan.cbrt + no.users + pc.pro + Business + 
                      inv.mlsto.log*pc.pro + inv.mlsto.log*Business,
              data=all7d,
            method = 'lm', trControl = tc)

#RMSE = 0.49246
#compared to non-cross validated
# RMSE = 0.4759
```

Not really trying to tune anything via cross validation, however RMSE increased from 0.4759 to 0.49246.

Not THAT bad.

Now, how to get variable importance from lm..

```{r, echo=FALSE}

#variable importance for full variables only - pairs.lm
#use varImp from caret package - uses t-test statistic

imp<- varImp(pairs.lm, scale=FALSE)
imp$variable<- rownames(imp)
imp<- imp %>% select(variable, Overall)
imp %>% arrange(-Overall) %>% head()

sum(imp$Overall)

Trial some scenarios:

Run full variables plus

Make a function to output:

* var importances
* RMSE

based on a list of variables that you want to use

```{r, echo=FALSE}

sample<- all7d[1000,]
sample<- sample[,!is.na(sample)]
vars<- names(sample) 
vars<- vars[! vars %in% c('mlsto','Year','inv.mlsto','timespan','client.totinv','code.director','Num.disc','Biz.type','Post.Code',
               'code.ProjEng','return.pdol','cost.mlsto','hrs.mlsto','balance.mlsto','client.totinv.log','pc.majpos')]
vars

RMSE<- function(answer, guess){
        error= answer-guess
        root.error= sqrt(mean(error^2))
        # print(root.error)
}

final.output<- function(df=all7d, samp = 800) {
        #create sample df
        sample = df[samp,]
        sample = sample[,!is.na(sample)]
        vars= names(sample)
        vars = vars[! vars %in% c('mlsto','Year','inv.mlsto','timespan','client.totinv','code.director','Num.disc',
                                  'Biz.type','Post.Code','code.ProjEng','return.pdol','cost.mlsto','hrs.mlsto',
                                  'balance.mlsto','client.totinv.log','pc.majpos')]
        variables = vars

        print(
                list("sample case", t(sample %>% select(-Year, -timespan.cbrt, -inv.mlsto.log, -client.totinv.log, -pc.majpos.log)))
        )

        #make reduced dataset with complete cases for all variables we want to use
        reduced = df[complete.cases(df[,variables]),]

        print(
                paste(nrow(reduced), "cases in full model")
        )

        formula = paste("return.pdol ~ ")

        for(i in 1:length(variables)){
                formula = paste(formula, variables[i], sep= " + ")
        }

        if('inv.mlsto.log' %in% variables &
           'inv.mlsto.log' %in% variables){
                formula = paste(formula, 'inv.mlsto.log*pc.pro', sep= " + ")
        }

        if('inv.mlsto.log' %in% variables &
           'code.client' %in% variables){
                formula = paste(formula, 'inv.mlsto.log*code.client', sep= " + ")
        }

        if('JD.Second' %in% variables &
           'no.users' %in% variables){
                formula = paste(formula, 'JD.Second*no.users', sep= " + ")
        }

        final = aov(as.formula(formula), data = reduced)

        fit= summary(final)

        ans= data.frame(answer= reduced$return.pdol, final.lm = predict(final, reduced, interval= 'predict'))

        # print(head(ans))

        #print variable importances for reduced lm just run

        imp= data.frame('vars'= rownames(fit[[1]]), 'F.val' = fit[[1]]$`F value`)
        #remove white space from levels in imp$vars
        levels(imp$vars)<- sub("\\s+$", "", levels(imp$vars))
        #remove Residuals row
        imp= imp[!(imp$vars %in% 'Residuals'),]

        #print variable importances
        print(
                list("variable importances",
                     imp %>% arrange(-F.val) %>% head())
        )

        #print RMSE for cases that match certain categories only
        #first subset predictions to cases that match the category

        reduced$predict= ans$final.lm.fit

        cats= c('code.client', 'code.contact', 'JD.Second', 'Business', 'Discipline', 'majority.pos')

        for(i in 1:length(cats)){
                if(cats[i] %in% vars){
                        cats.red = reduced[reduced[,cats[i]] %in% sample[,cats[i]],]
                        cat.RMSE = RMSE(cats.red$return.pdol, cats.red$predict) %>% round(4)
                        print(
                                paste(cats[i], "RMSE =", cat.RMSE, sep= " "))
                        print(
                                paste("Number of cases =", nrow(cats.red), sep= " "))
                        print(
                                head(cats.red[,c('mlsto','inv.mlsto','cost.mlsto','return.pdol','predict',cats[i])])
                        )
                        }
        }

        final.RMSE= RMSE(ans$answer, ans$final.lm.fit) %>% round(4)

        print(
        paste("Overall predicted RMSE=", final.RMSE , sep= " ")
        )

        predict.rpdol = predict(final, sample) %>% round(3)
        predict.rpdol = predict.rpdol[[1]]
        predict.cost = sample$inv.mlsto/(1+predict.rpdol) %>% round(1)
        print(
               paste("return per dollar prediction", predict.rpdol, sep = " ")
        )

        print(
               paste("answer", sample$return.pdol %>% round(3), sep = " ")
        )

        print(
                paste("Invoiced= $", sample$inv.mlsto, ",   predicted cost= $", predict.cost %>% round(1), sep="")
        )

        print(
                paste("Actual cost= $", sample$cost.mlsto, sep="")
        )

}

final.output(df=all7d, samp = 500)

### 2015-08-21 cluster.rmd
getting somewhere with regression

# library('knitr', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('ggplot2', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
# library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
# library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
# library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
# library('car', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('fpc', lib='C:/Progra~1/R/R-3.2.1/library')
# library('vegan', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library(devtools,lib='C:/Progra~1/R/R-3.2.1/library')
# library('ggbiplot',lib='C:/Progra~1/R/R-3.2.1/library')
# library('RcmdrPlugin.BCA',lib='C:/Progra~1/R/R-3.2.1/library')
# library('FNN', lib='C:/Progra~1/R/R-3.2.1/library')
# library('caret', lib='C:/Progra~1/R/R-3.2.1/library')

@@

# 
# setwd("~/OneDrive/shared files/Bligh Tanner/masters/data")
# setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
# opts_knit$set(root.dir= "C:/Users/n9232371/Documents/Consultbusiness/data")
# all7c<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all7c.csv')[,-1]
all7c<- read.csv('~/OneDrive/shared files/Bligh Tanner/masters/data/all7c.csv')[,-1]
all7c$Post.Code<- as.factor(all7c$Post.Code)

@@

Create reduced dataset and have a think about what you want to cluster against each other

>>>>

library('knitr', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('ggplot2', lib = 'C:/Progra~1/R/R-3.2.1/library')
library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
# library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
# library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
library('car', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('fpc', lib='C:/Progra~1/R/R-3.2.1/library')
# library('vegan', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library(devtools,lib='C:/Progra~1/R/R-3.2.1/library')
# library('ggbiplot',lib='C:/Progra~1/R/R-3.2.1/library')
# library('RcmdrPlugin.BCA',lib='C:/Progra~1/R/R-3.2.1/library')
# library('FNN', lib='C:/Progra~1/R/R-3.2.1/library')
# library('caret', lib='C:/Progra~1/R/R-3.2.1/library')

@@

# 
# setwd("~/OneDrive/shared files/Bligh Tanner/masters/data")
# setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
# opts_knit$set(root.dir= "C:/Users/n9232371/Documents/Consultbusiness/data")
all7c<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all7c.csv')[,-1]
# all7c<- read.csv('~/OneDrive/shared files/Bligh Tanner/masters/data/all7c.csv')[,-1]
all7c$Post.Code<- as.factor(all7c$Post.Code)

@@

Create reduced dataset and have a think about what you want to cluster against each otherim

### 2015-08-21 var_select.rmd
big dump started regression
getting somewhere with regression

State- impute QLD
Business - 22 NA values - impute 'unknown'
Biz.size - 38 NA's - find median, impute?
Biz.type - 18 NA's impute???
charge.ph - delete
charge.pc - delete
Start.Date - delete
End.Date - delete
no.users - 4 NA values - impute
pc.usersss - 7 NA's - what to do. 0 for all? averages for all?
Num.disc - 84 NA's - impute 1?
num.inv and mean.inv- 1 NA?

@@

@@

# write.csv(all7b,'all7b.csv')
all7b<- read.csv('all7b.csv')[,-1]

>>>>

State- impute QLD
Business - 22 NA values - impute 'unknown'
Biz.size - 38 NA's - find median, impute?
Biz.type - 18 NA's impute???
charge.ph - delete
charge.pc - delete
Start.Date - delete
End.Date - delete
no.users - 4 NA values - impute
pc.usersss - 7 NA's - what to do. 0 for all? averages for all?
Num.disc - 84 NA's - impute 1?
num.inv and mean.inv- 1 NA?
code.ProjEng - impute: all from pre 2005. All projEng can = director for that job
code.director - impute only 'unknown' to be S121 - by far the majority and fits job description

@@

#impute code.director Unknown to be S168
all7b[all7b$code.director == 'Unknown',]$code.director<-'S168'
all7b$code.director<- droplevels(all7b$code.director)
#impute code.ProjEng to be Director codes for that job
all7b[is.na(all7b$code.ProjEng),]$code.ProjEng<- all7b[is.na(all7b$code.ProjEng),]$code.director
all7b$code.ProjEng<- droplevels(all7b$code.ProjEng)

@@

write.csv(all7b,'all7b.csv')
all7b<- read.csv('all7b.csv')[,-1]
